Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-26 6-ModelPresentation.tex
Updates from Overleaf

    abstract concept Gateway extends Type {
      abstract void executeGateway(Process process);
      ...
    }

@@

\begin{lstlisting}[breaklines=true, language=java, basicstyle=\ttfamily\scriptsize, mathescape=true]
forEach (actor : performingActors) {
    assert isAuthorizedActor(actor);
}
\end{lstlisting}

@@

\begin{lstlisting}[breaklines=true, language=java, basicstyle=\ttfamily\scriptsize, mathescape=true]
concept ActorType extends Type {
 ActorType[0..*] parentActorTypes;
 ...
 boolean isOrSpecializes(ActorType actorType) {    
  if (actorType == this)   
   return true;      
  for (p : parentActorTypes) {      
   if (p.isOrSpecializes(actorType)
    return true;        
  return false;    
 }
 ...
}

>>>>

    abstract concept Gateway extends Type {
      abstract void execute(Process process);
      ...
    }

@@

\begin{lstlisting}
forEach (actor : performingActors) {
  assert isAuthorizedActor(actor);
}
\end{lstlisting}

@@

\begin{lstlisting}
concept ActorType extends Type {
  ActorType[0..*] parentActorTypes;
  ...
  boolean isOrSpecializes(ActorType actorType) {    
    if (actorType == this)   
      return true;      
    for (p : parentActorTypes) {      
      if (p.isOrSpecializes(actorType)
        return true;        
      return false;    
    }
 ...
}
